dbRDA analysis

### 2017-04-17 doc/RMD/RDA-analysis.Rmd
update dbRDA figure

  mul     <- arrowMul(dbsum$biplot[, 1:2], dbsum$sites)
  Arrows  <- data.frame(dbsum$biplot * mul)
  Arrows  <- rownames_to_column(Arrows, var = "class")
  Arrows  <- mutate_(Arrows, .dots = list(Length = ~sqrt(CAP1^2 * CAP2^2)))
  Arrows  <- arrange(Arrows, Length)
  Arrows  <- top_n(Arrows, 8)
  ggplot(Centroids, aes(x = CAP1, y = CAP2))+
   geom_point(data = SampleCentroids, alpha = 1/2, fill = "dark orange", color = "black", size = 2.5, pch = 21)+
   coord_cartesian() +
   geom_segment(aes(x = 0, xend = CAP1, 
                    y = 0, yend = CAP2),
                arrow = arrow(length = unit(0.3, "cm")), 
                data = Arrows
                ) + 
   geom_label_repel(aes(x = CAP1, y = CAP2, label = class), data = Arrows)
}
```

@@

# Plot the results
```{r}
plot_dbrda(cap11cc) + theme_bw() + theme(text = element_text(size = 14))
plot_dbrda(cap16cc) + theme_bw() + theme(text = element_text(size = 14))
```

>>>>

  terms   <- paste0("(", paste(attr(db$terms, "term.labels"), collapse = "|"), ")")
  mul     <- arrowMul(dbsum$biplot[, 1:2], dbsum$sites)
  Arrows  <- data.frame(dbsum$biplot * mul)
  Arrows  <- rownames_to_column(Arrows, var = "class")
  # Making the classes presentable
  Arrows$class <- gsub(terms, "\\1: ", Arrows$class)
  Arrows$class <- gsub(": $", "", Arrows$class)
  Arrows$class <- gsub("unk", "unknown", Arrows$class)
  Arrows  <- mutate_(Arrows, .dots = list(Length = ~sqrt(CAP1^2 * CAP2^2)))
  Arrows  <- arrange(Arrows, Length)
  Arrows  <- top_n(Arrows, 8)
  ggplot(Centroids, aes(x = CAP1, y = CAP2))+
    geom_point(data = SampleCentroids, alpha = 1/2, fill = "dark orange", color = "black", size = 2.5, pch = 21)+
    coord_cartesian() +
    geom_segment(aes(x = 0, xend = CAP1, 
                     y = 0, yend = CAP2),
                 arrow = arrow(length = unit(0.3, "cm")), 
                 data = Arrows
                 ) + 
    geom_label_repel(aes(x = CAP1, y = CAP2, label = class), data = Arrows) +
    ylab("Eigenvalue 1") +
    xlab("Eigenvalue 2")
}
```

@@

# Plot the results
```{r resultplot, fig.width = 5, fig.height = 5}
cap11cc
cap11cc$anova
plot_dbrda(cap11cc) + 
  theme_classic() + 
  theme(text = element_text(size = 14, color = "black")) +
  theme(aspect.ratio = 1)
ggsave(filename = "results/figures/publication/Figure7Z.svg", width = 88, height = 88, units = "mm", scale = 2)
cap16cc
cap16cc$anova
plot_dbrda(cap16cc) +
  theme_classic() + 
  theme(text = element_text(size = 14, color = "black")) +
  theme(aspect.ratio = 1)
```
